
\section{Street Network}



outline:
\begin{itemize}
  \item
  what and Why?  The power of the physical, local, and free.  Organic media, what we want, links to previous chapter.  Universal social media for sharing of information in a physically local domain with both content creation and consumption on all Web-enabled devices(laptops, phones, tablets, etc.)  Hybrid markets: like Craigslist, but way more local.  General description of what the system does(scrolls,maps, feeds, symbols, apps, industrial design and production via Trash Robot). This points to the subsequent chapters about these actual things.  Free boxes and food not bombs.  We are a hybrid between free boxes and food not bombs and craigslist.
  \item
  The Terminal.  This is the heart of this system. What is the Raspberry Pi, why is it powerful?  How to build the Terminal. Options involving big screens and projectors, public terminals with large publicly viewable displays.  How to adapt it to different situations, how to work with wifi networks, IP addresses, local and global, opening up a local wifi to a public domain.  how to avoid ANY property.  How the terminal is passed from user to user to operator to operator.  Data hygiene: how to keep all personal information of any kind of the machine, to prevent leaks of property.  What it means to have a network without property.  Replication paths via local laptops(localhost) on wifi, global github repos, replication to global hosted domains. How to constantly back up and replicate to avoid information death.  How to kill bad information.  How to nuke the whole system if it's too rotten.  Grey market and black market commerce.
  \item
  The Operators, what we are, what we do, how we do it, how we make money and barter, how we train new Operators .  Role of Operator as universal moderator.  Forking and avoiding the trap of the network monopolist.  How to transition between money to barter, how to scale up to an all barter system by providing value for 
  \item
  Psychogeography.  Nodes of power, examples at global level and local level, finding the nodal points.  Go through the whole philosophy, places, examples such as: parks, intersections, neighborhoods, famous landmarks, bridges, forking below a place, discussion of distance scales and granularity.  Targeting nodes of power: Sand Hill Road. Wall Street. SoMa.  K Street DC. Jackson Hole. Martha's Vinyard.  Navy Memorial DC. Use of power nodes to build extremely powerful local networks, where information is exchanged between players in existing power networks.  A network in the right coffee shop could connect people who collectively are processing 10's of billions of dollars of commerce just in that one coffee shop!
  \item
  domains.  choosing domains, buying them, sharing them, avoiding troubles. Entropy of domain choice, size of name space. use of free web hosting services.  Signs, markers, stencils, postcards: physical media which points to domains which point to terminals and link to the IP addresses.  The work flow with physical media to software media and back.
  \item
  The market
  \item
  the coffee shop(or pub) node.  How it can build community in the coffee shop, help all coffee shop customers to share and prosper, help neighbors of coffee shop, the developer workflow, use to expand operators.  Coffee shop network as service for coffee shop owner for barter for coffee and food at shop.  Building collaboration with businesses, both local and global, how to use global chains to scale globally with mutual aid and benefit for all.
  \item
  scaling up: the global swarm, going to full stack geometron(see last chapter), building more 
\end{itemize}

\subsection{What is the Street Network?}

We want an information network based around physical replication of technology from trash.  To stimulate the replication of the Network, we need it to create value for people who use it and operate it. This value can be of many kinds: it can directly provide physical goods people need, it can facilitate business in the monetary economy, it can provide mutual aid to a community, it can create local social connections, can build network power for users, and any of these values can be traded for materials and space needed to continue to expand the network.  

Truly free network. The Humble Pi.  The power of a network without property or users.  Networked technology with free sharing can create more value for users than one with private data.  Destroy the data brokers by making a network with no personal data.   

This book will describe several products and services which Operators in the network can provide to local users.  These can be exchanged for money or bartered directly for materials to expand the system(for instance one can ask users who are paying for goods or services to simply buy more computer equipment to build out more network infrastructure.)  We aim to have the goods sold be as much as possible based on a stream of trash which are upcycled into sellable products.  The prototype product here is a purse, the ArtBox, which can be constructed using the methods of Geometron and which contains the tools to replicate itself.  It is, in essence, a self-replicating purse with a unique Open Brand, the Trash Robot Brand, which will be documented in its own chapter.  

Services rendered will generally be of the kind which makes money for the user.  So for instance a passerby might place an advertisement on a news scroll for a local coffee shop for their service which other coffee shop customers(this is all over the wifi network of the coffee shop so everyone is indeed a customer) might want.  This makes the user money, which motivates them to come back and place more ads, so they are making money which they can pay to the Operator.  All of this commerce then motivates people to come into the coffee shop and read and share documents.  Since wifi has a time limit and requires purchase, this brings higher traffic to the coffee shop, which then has their revenue go up, so to keep the system running, it is worth it to them to barter snacks and coffee to the Operator of the network.  

Structure and purpose of the network: domains, places, operators, mutual aid, markets, 

Networks are advertised with physical media which points to domains which point to physical places, specifically to the location of the physical web server, and have a hyperlink which only works on the local wifi network which links to the web server on that network.

The Street Network is social media based around physically local instances of the Web which are not on the public Internet.  Wifi networks are used to share documents locally with other users on the same network.  The Geometron servers function as public bulletin boards, where documents are shared freely with all other users. Any user can edit or delete any file. All files can be copied by anyone.  Documents are all visible by both mobile devices and computers, as long as they are on the same wifi network.  The Street Network is an example of Organic Media. It is intended to facilitate replication by users.  Users can create and share documents advertising whatever commerce they wish to engage in: they can sell things, share ideas, give things away for free, advertise services, advertise businesses, describe how to make things, or look for others with shared interests.  There are no users and no databases.  There is just a list of documents which users can click on to read, edit using the editors or delete using the file deletion tools.

The Geometron documents are stored on a Geometron Terminal, which is based on the Raspberry Pi mini-computer.  Raspberry Pi is a non profit project from the UK to create a minimalist Linux based computer, mostly for education, research, art, and maker hobbies.   They can be purchased easily online for approximately 50 US Dollars.  The two most widely used formats of Geometron documents are the Scroll and the Map.  A scroll is just a text file, with some formatting in a markup language called Markdown.

Add paragraph somewhere on role of cryptography in sharing encrypted plain text copy/pastable files.  add functionality.  PGP?  ask someone for help on this section to get it right. How does this all work with various crypto technologies?  free sharing of encrypted files which can be replicated but then decrypted privately.  This can be a huge vector of replication for the crypto community, including inside the formal and informal intelligence community.  

what does the server do, what is an app, what is a document, overview of symbols, maps, scrolls,data,apps,automation.

Edit scrolls.

Edit maps.

feeds.  using feeds.

Workflow, developers, apps.  reference code structure chapter. Coffee shop developer community.


\subsection{Users}

We are looking to build a network which promotes the development of physically local power structures.  To that end, we choose nodes of physical power, such as the most important locations in global cities like key traffic circles in Washington DC.  We then study \emph{all} the stakeholders in that physical location. This includes residents, tourists, people walking through, truckers, commuters, workers, panhandlers, local homeless, business owners, the local mail carrier--really everyone, but restricted entirely based on that physical place, rather than any other affiliation.  Our network seeks to give the power of networking in that place to everyone in that place. As more people join, more infrastructure is added, until an entire ecosystem of interconnected network nodes grows up in some cases around just a single street corner(say 16th and Mission for example in SF).   

The network has to start somewhere, however.  We start with Trash Robot, operating the robot to make and sell tokens, and selling all the parts of Trash Robot.  We can recruit people to learn the system who can immediately sell Trash Robot elements to make money, which will lead to replication of the network.  Since Trash Robot uses the Geometron system to design the symbols, share how to build the robot, program the robot, etc., the social media system will be automatically replicated as Trash Robot replicates.  If the network replicates and Trash Robot Operators learn to operate the Geometron servers, the network will grow, and like all networks its power and value will increase exponentially with size.  We also initially need developers to improve the code and build out the more technical elements of the system, essentially setting up Raspberry Pi based web servers and distributing them.  So initially we need two groups of people: people to build and sell the elements of Trash Robot and people to develop applications for the Geometron system, build servers and distribute and install them.  In both cases, Trash Robot builders and Developers can be recruiting Operators who have less specialized skills but can make money from the system via simple means of just stamping out more and more tokens from already-printed stamps or posting ads for people for money on a bulletin board they operate but did not set up.


Trash Robot Makers: build trash robots.
Trash Robot  printer Operators: run the robot to print.
Trash Robot artists: design new symbols
Trash Robot market Operators: operate a bulletin board



Geometron Developers.    Geometron Operators.


A Geometron station can have a huge display which all passerby can read without even loggin on, also.

In order for this network to grow it has to create value for people. The more people it provides value for and the more value it provides, the more effectively it will replicate.  I will now discuss some of the specific groups of people who can benefit, how they can use the network, and what the benefits are for them specifically.

Traveling kids, hobos, panhandlers, people asking for money or selling things on the street corner.  A physically local free bulletin board shared by passerby in a high traffic area can allow people asking for money who are currently ignored by passerby as just another anonymous face and cardboard sign a chance to really tell their stories and to share all that they have to share.  When people share their stories they can become part of the emergent physical community of passerby in a location where the network node is located.  When people view others as part of their community they not only are more willing to help, they can have open communication about the best way to help, expanding from just spare change to more comprehensive mutual aid.  Because we clone content from the local terminal to web pages on globally visible domains linked to a physical place, which are advertised everywhere in that place, marginalized people whose only ability to get online is the public library can use the computers there to get the information they need to better survive, and ultimately to thrive and build new communities where they already are.  The way a local network can help people is twofold. First, it is direct, by asking for money and other mutual aid.  But by being physically on location all the time, already with physical media(cardboard signs), people in a given place can aid the network, creating value for the other people in the community who are more resourced, who then no longer view monetary support as ``donation'', but rather as an expense which supports their other business activities.  

In order to see the power of this second means of network support of marginalized people on the street, we have to look more closely at the network nodes we are building.  One of the major types of node is in a business district of a city where there are both homeless people asking for money, on the street all day with physical media, and power brokers who make their living entirely from connections.  These people include venture capitalists, entrepreneurs, lobbyists, consultants, and the rest of what might be called the ``deal-making class''.  An example of this confluence is some of the parks along K-Street in Washington DC.  K Street and adjacent streets is home to a huge homeless population as well as power brokers whose livelihood depends entirely on connections.  If a physical network were built which facilitated direct communication between people along K Street, the people who spend the most time physically on the street can be brokers of information on a network which can be worth a lot to the people who trade in information.  Physically local information networks can leverage the power of physical places with very powerful people walking past all the time who normally never communicate.  Connecting these people up can be dangerous.  But if we provide them with value, it can be worth a both a lot of money to them and also potentially something they can barter for giving us space to live and work nearby.  If you facilitate a 10 million dollar deal and the customer knows you can do it again, the least they can do is give you a 100 dollar gift card to the nicest restaurant in the block.  There is no real upper limit on what an enterprising Network Operator could in theory make if they learned to really channel information efficiently in the nodes of global power.  And of course we must remember that when dealing with power brokers their currency is not money.  When the people who currently have the most power in society find themselves dependent on free open networks, those networks themselves will gain power which penetrates that of the existing power structures, potentially creating an existential threat to them.  We must take note of this.

The elements of traveler culture which overlap with ``van life'' are also key to increasing the network effects of the Street Network.  This also links to trucker networks.  People who live their lives on the road can use this network infrastructure to set up complex networks and markets in highway rest stops, Walmart parking lots etc. using either wifi networks in these places.  These networks can be of utility to passerby of all kinds, from tourists to truckers to the workers who keep the places running.  Just as existing global social media networks provide value they can charge money for, a physically local network can provide value which people will pay for.  An example use case here is a Street Network Operator agreeing to maintain a backup of and keep posting an advertisement for something a local entrepreneur is trying to sell to truckers.  In exchange for that, they can get directly compensated in gas, right there in the rest stop, without money changing hands.  


Food not bombs, street outreach, harm reduction people, mutual aid workers.  See above.  The people who are working to help the most marginalized members of any given community can better reach that community if there is a physically local media platform where people can share information about resources.  Documents can be posted which explain how to get access to resources, when and where resources will be available, etc.  Because the whole system self-replicates, as with Food Not Bombs, anything which is successful in any given place can be immediately cloned to other nodes on the network.  Food Not Bombs already has a global network of free and open nodes with no property but a very recognizable brand identity and set of behaviors and actions.  FNB nodes are generally already linked by networks both online and via people who travel from one punk house or FNB house to the next.  The whole anarchist network of community houses, FNB's, anarchist infoshops and bookstores, really really free markets, free boxes, etc. can form a basis for a truly free information network carried from house to house and city to city, running on house wifi networks.  

Coffee shop owners.  Building a network in a coffee shop on the wifi network which requires purchase to use and which has a time limit can create a huge amount of added business for any local business owner.  It also builds community. So coffee shop owners who find themselves with a full shop of laptop drones with headphones on who work for hours, or get kicked out and do the same thing somewhere else can instead find themselves the brokers in a very powerful information network.  Much of the commerce of the world is now code written in coffee shops on laptops.  Creating physically local networks around these already existing groups can create huge power for the users which then benefits the people who set up the infrastructure(again, just like existing centralized social media platforms.)

Developers.  We need developers to be constantly writing more and better software in order to make Geometron a success. Developers who work all day in coffee shops or any other shared space like a co-working space or pub can have a social network based on both co-developing applications useful to all and sharing other resources.  Developers will use the resource of the Street Network terminal/server on the local network in the same basic way as others: they can share their resumes, links to pages of personal projects.  Developers are key to the whole system. We must recruit developers with this book who will rewrite all the code and also the book, replicating the whole system.  The faster our network can get developers into the swarm, the faster the code itself will improve.  Developers are key!!  Developers create servers to share into the network.  

Power brokers. Venture capitalists, financiers, entrepreneurs, deal-makers of all kinds, lobbyists, politicians.  Your network is your power.  Geography matters.  Build a network in the lobby.  Post things on street nodes, build your network, build your power, build your literal street cred. Dealflow.  

Crafters, makers, jewelers, artists.  An alternative to Etsy, street vending, or being in a shop.  Post your stuff to the local networks.  This is much more free and long form than existing platforms, you can post images, descriptions, contact info, times and places when you'll be in a place.  This can be way easier than other sales channels for arts and crafts.  You can say when and where you'll be at a place, post a link for contact, and then show up in the network node like a coffee shop to make the physical exchange.  In many cases, because the network is physical and local, there will be barter opportunities as well as direct sales.  A barter economy can develop where people donate materials you use for your crafts as part of how they pay for the finished product.  Removing shipping or transport costs by dealing directly in a physical location removes friction from the market, amplifying dramatically the power of the market, especially for crafts which involve physically bulky objects.  For instance, people can bring in motors and properly prepared plastic sheets and cardboard, as well as rolls and rolls of duct tape, and we can exchange finished products built from these materials and tools, as well as free food, drinks, and supplies, creating a market economy without money as well as without formal business structures(making it easier for marginalized people to participate).

Any labor pool of gig economy workers focused on a specific geographic location.  The most obvious of these is the drivers who presently drive for the major rideshare apps who all congregate at the airport to pick passengers up in the same exact place, and yet all of it is currently coordinated via the apps(unless you do the cab line).  The rideshares apps have proven that cities will ignore illegal cabs if they're done at scale.  It would be straightforward for a small team of Network Operators to run a server which replicates to a page which is advertised around, something like a domain of yourairportnamerides.xyz, which tells users how to log onto the wifi network created by an Operator's hotspot near the pickup zone and with a link on the page to the local network address of the server.  All all this IT is doing is directing customers to a dispatcher who manages the drivers over a simple app shared by the collective.  The whole network is run by a team of about 2-4 people.  One person might be a developer, who creates the app to manage all the drivers and post messages from dispatch.  Another person is all marketing, putting up the relevant information in the right places to get seen by travelers but not stopped by the rideshare apps, airport authorities, or the cab companies.  Riders will never have their destination information on the public network, nor will drivers put personal information, but they can work on an open trust model where they are known by dispatch, who has code names for them, and operates a queue app which simply adds drivers as the arrive near the Airport and pushes the most senior driver to the top of the stack, which is passed along to a rider.  Another Operator might be the one who runs the trust network for the drivers, verifying everyone and organizing meetings for the whole cooperative.  This can be used to unionize existing workforces quickly as well, building ad hoc networks which are very hard to suppress visible to everyone on their mobile devices on a local wifi network.  

The same model holds for places where workers congregate looking for short term construction work.  Those locations can have a server where an Operator runs a labor marketplace where a much larger and deeper labor pool can now advertise, but without all having to be in the physical location.  This means a crowd of a dozen workers looking for work can be replaced by an Operator with a sign pointing to the domain where the copy of the market is hosted.  Workers who come by can leave an ad on the local Raspberry Pi Geometron server, and anyone coming by looking for construction labor can just scroll through a now much deeper collection of ads and call whoever they need to hire.  A market place like this can suddenly go from a dozen general laborers to a construction labor market which includes specialists like plumbers and electricians as well as much larger general contractors just looking to save on marketing costs.  A person holding a cardboard sign on a street corner by a giant box home improvement store can now potentially be the broker of an information network on which millions of dollars of commerce flow.  


Trash Robot.  Trash robot will be described later in this work.  It is a system of technology which can be used to build products from a combination of waste streams and consumer off the shelf(COTS) products, which has a clearly recognizable brand identity owned by no one and provides value to an end consumer.  Trash Robot is a meta-business: a system for people to build businesses which can use both barter and sales to make money on the Geometron Street Network, further facilitating the replication of that network. If the right people start doing Trash Robot on the Network, we can create a system which has a significant consumer demand.  Trash Robot is structured to be very easy to replicate for an individual but very hard to replicate for a for profit centralized technology company driven by building up value in their equity.  This means if we can build up a significant consumer demand, it will provide a very powerful stimulus to replicating the nodes to grow our network, always as a free decentralized system.  Building a thing that replicates faster than property that is not property is how we start building a society without property.  This is described in detail it its own chapter later in this book.

Trash Robot is the most obvious way for those of us who are building this network to exist.  Other people might be Operators, developers, or participants in various markets, but the Trash Robot is the heart of the hardware development which this whole self-replicating social media platform is designed to replicate.  Trash robot is the reason we are building the Street Network and Geometron information system.  Trash Robot is a system of technology which provides value to people of a variety of kinds.  But because it allows Operators of the Trash Robot to be able to print nice clay tokens printed with arbitrary icons designed on the system, we have the ability to issue our own symbolic currency, which can create a new geometric economy not based on money but with some similarities.  We will build clothes with an open brand people can use to replicate their own copies.  We will make interesting or useful accessories like purses, machine carrying bags, and jewelry. We will make and sell robots, and teach classes on how to make them and use them.  And we will make the icon tokens to mean anything and exchange for anything. 

The tokens printed on the Trash Robot printer are totally unlike money.  They have no numerical value of any kind.  What they have is simply two symbols, both created in a universal geometric language which can be copy/pasted freely across the Network.  If someone sends you a text message with a string of numbers separated by commas and you give that to the Operator of a Trash Robot Icon Token Printer, they can just paste that text into their browser, use the code in there to program the Robot Printer and print the pattern into clay from the code. Also, the coins are all themselves self-replicating without the printer.  Because they have depressions along where they are printed, clay can be molded around the depressions to make another clay token which has the inverse of the pattern in it but with raised clay instead of depressed. When this piece of clay is baked, it can then be used to print another token, making an exact copy of the original.  This can be repeated many times. Thus printing one coin with a Trash Robot Printer can propagate out to in theory a very large number of copies.  Copies might degrade as more and more are made but if each copy is used to make many copies and so on, in a giant tree, one can easily imagine one print making thousands of tokens with no more use of the printer!  Again, we have made self-replicating media, both self-replicating online where we can share the code which does the print and self-replicating in the physical manifestation where the clay objects are used to make more clay objects.

\subsection{Building the Geometron Terminal/Server}

These should be called servers because they're servers.

Buy the stuff:

\begin{itemize}
\item
Raspberry Pi 4 board from Sunfounder
\item
SD card
\item
SD card reader
\item
Mini USB keyboard(without number pad)
\item
mouse
\item
Sunfounder HDMI display with 12 volt power supply and USB power out to drive PI, wall plug and HDMI cable, or similar display which can run off of a 12 volt barrel connector with a USB power output to drive the Pi.
\item
12 V LiPo battery pack with wall plug charger from TalentCell(sold via amazon)
\item
wifi hotspot
\end{itemize}

Put it together.  Just assemble the Sunfounder terminal as per the instructions.  

If you have a display that does not have a mount for the Pi, build an integrated terminal with cardboard, duct tape, and plastic HDPE sheet from milk bottles.

Burn the card with NOOBS, put it in the Pi.

Use paint pens to put symbols on keyboard.

plug in mouse and keyboard.

Make a bag to carry the terminal around in, or find an appropriate backpack and sew symbol onto it.  Symbol of Raspberry Pi using Penrose Tiles.

Boot up the pi, set it up with no password

Install Apache and php

copy the Geometron code replicator script replicator.php into the web directory. THis can be found from any geometron server at [serverurl]/php/replicator.txt.  

Learn to use with subsequent chapters of this book, customize and deploy, replicate to other people

run in headless mode, or on big screen, discuss display options, how to deploy in different places


\subsection{The Operators}
Building a relationship between Operators and Developers.  Operators deal with people and information.  Developers deal with code and build the apps to allow operators to operate. Operators connect people: passerby, shop owners, truckers, workers, drivers, developers, community members, other operators.  The Operator is like a switch board operator in the old Bell phone system before automated switching.  Switch board operators in small towns before automation knew not just phone numbers but the structure of the town, who was likely to be where, who gets called a lot, and in general how information flows through the networks of the town.  This role is very old, however and has been held by pub keepers, religious figures, coffee house owners, and numerous others throughout history and throughout the world.  The role of the information exchange manager is one all societies need.  The Geometron system creates a specific way for someone to carry out this role in a geographic location, which is easy to replicate in other locations, and to share information from place to place.

The relationship between Operator and Developer is key to structuring the network in a way that scales.  Both roles have to be self-replicating in that Operators recruit and train Operators as well as find new people to get trained as Operators


\subsection{Psychogeography}

Introduction, what is Psychogeography, the historical references to the situationists.  

Coffee shops and the laptop classes.

Global power nodes. examples.



\subsection{Domains}
\subsection{Street Market}
We help people sell stuff directly on the Street, out in the open, with a sign advertising the Market.  People can sell for barter.  We also sell directly the items from Trash Robot and other Geometron Things described below.  These include the ArtBox as a purse, shirts, pants, flags, bags, clay icon tokens, robots, terminals, laser cut acrylic shapes and rulers and protractors, Pyramids,.
\subsection{Coffee Shops and Pubs}



\subsection{Scaling Up}


Street Network:

\begin{itemize}
  \tightlist
  \item
  operators  
  \item
  terminals
  \item
  domains
  \item
  streets
  \item
  places
  \item
  developers
  \item
  signs
  \item 
  postcards
  \item
  markets
  \item
  feeds
  \item
  scrolls
  \item
  maps
  \item
  pages
  \item  
\end{itemize}






The \href{scrolls/terminal.md}{Terminal} is a
\href{https://www.raspberrypi.org/}{Raspberry Pi} with a keyboard,
mouse, display and power supply, which run a web server only visible
over the local wifi network. It is carried by the Operator, who uses it
to help users create, edit, copy, and share files over the local
network.

The files on the Network can be: - \href{scrolls/scrolls.md}{Scrolls}.
These are a type of text file which uses the
\href{https://daringfireball.net/projects/markdown/}{Markdown markup
language} for formatting.\\
- \href{scrolls/feeds.md}{Feeds}. Feeds are either a directory with a
sequence of files a user can scroll through and select or an array of
any kind of information, be it images, symbols, words, links, etc. -
\href{scrolls/maps.md}{Maps}. A map is a sort of generalized meme, like
a PowerPoint or Keynote slide. It is an array of elements each of which
has a position, angle, width, possibly an image url, some text, and
possibly a link destination, which might be either a HTML hyperlink or
an internal link to a file on the system

All users on the same wifi network as the Terminal can view, edit,
delete, and copy all the files on the system. There are no user names,
no logins, no passwords, no private data, and no databases.

Users can all see all files, edit them, delete them, copy/paste them,
create new ones

Operators carry the Terminal around, share its link with people, talk to
people about the system, teach users to use the system, help to share
with new Operators.

Roles of the Operator:

\begin{itemize}
\tightlist
\item
  the keeper of the physical Terminal
\item
  maintain relationships with users of the Terminal and Domain
\item
  update the Geometron server at the hosted Domain with links to the IP
  address on the local wifi network of the Terminal, as well as the wifi
  network name and password or link to where to get it(e.g.~coffee shop
  register)
\item
  post ads for money or barter on the Geometron server at the hosted
  Domain for people who ask
\item
  post on the global Geometron server when and where the Operator will
  appear, or where the terminal is set up on what network if it's
  installed permanently.
\item
  Teach anyone who wants to learn how to be an Operator, recruit new
  Operators
\item
  Tell new users about the Network, teach them to use it, how to post,
  edit, delete
\item
  Promote any kind of business or other venture or project anyone
  physically local to the wifi network area has in exchange for barter
  with that user for useful things on location(including just a place to
  operate)
\item
  Spread Network into new places by finding a location with a wifi
  network, buying a domain and setting up hosting or getting someone to
  do that and pay for it,
\item
  Domain names spread in physical space using physical media with
  depiction of domain which points back to terminal ip address, wifi
  address and password, photo of terminal and operator other physical
  media(post cards, book marks, spray paint stencils), spreading the
  physical media with the domain name
\end{itemize}

Skills of Operator

\subsection{Domains}\label{domains}

\subsection{Terminals}\label{terminals}

\subsection{Laptops}\label{laptops}

get ubuntu working under windows, install apache and php

localhost

code goes from terminal to laptop to github to
